---
title: "R Markdown Demo"
output:
  html_document: default
  pdf_document: default
---

In this demo we continue to work with the starwars data 

##Packages
We start with loading the packages we'll use.
```{r load-packages, message=FALSE ,warning=F}
library(tidyverse)
```

First, let's try to `knit` this R Markdown file to a html file. Click on the `knit` button on top. It should open a html page.

In class, we have seen these two plots. Now each member of your group can choose one block and modified the code with in that block to show a plot with only two genders, male and female. You can also choose between `knit to html` or `knit to pdf`. Compare your knitted html/pdf with your other member of your group. Let us know if you encounter any error.

1. Segmented bar plots, counts
===========
```{r}
ggplot(data = starwars, 
       mapping = aes(x = gender, 
                     fill = hair_color)) +
  geom_bar()
```


2. Segmented bar plots, proportions
===========

```{r}
ggplot(data = starwars, 
       mapping = aes(x = gender, 
                     fill = hair_color)) +
  geom_bar(position = "fill") +
  labs(y = "proportion")
```


3. Segmented counts/proportions plots
===========
```{r}
newData<-starwars[starwars$gender %in% c('male','female'),]
glimpse(newData)
```

4. Knit to PDF
=========
To be able to knit PDF file from Rmarkdown. Try run the following lines. You will see a warning message saying two error messages will be displayed. Acknowledge it. After two error messages and a long installation process, you should have the ability to generate PDF from Rmarkdown files.
**You may want to do this after the class today, you will need the Rstudio to complete the group lab**
```{r, eval=F}
library(tinytex)
tinytex::install_tinytex()
```

To check if you have install successfully. Run these lines in your console. You should see an output of 
`[1] "test.pdf"` and a `test.pdf` now in your folder.
```{r, eval=F}
writeLines(c(
  '\\documentclass{article}',
  '\\begin{document}', 'Hello world!', '\\end{document}'
), 'test.tex')
tinytex::pdflatex('test.tex')
```


